Velocity Inversion by Surface Source Extension

### 2020-02-02 repro/papers/ssevelan/paper.tex
trans to srcextcv

A simple example: acoustic transmission inversion - isotropic point radiator (``source'') located at  $\bx=\bx_s$
\begin{equation}
\label{eqn:awept}
\frac{1}{\kappa}\frac{\partial p}{\partial t} = -\nabla \cdot {\bf v} + f(t)\delta(\bx-\bx_s), \,\rho \frac{\partial {\bf v}}{\partial t} = - \nabla p; \,p,{\bf v}=0, t \ll 0
\end{equation}
Bulk modulus is depicted in Figure \ref{fig:bml0}.

\plot{bml0}{width=\textwidth}{Lens example: target bulk modulus $\kappa$}

@@

%\includegraphics[height=1.5in]{Fig/pulse00.pdf} %\includegraphics[height=1.5in]{Fig/ptpwindl0.pdf}\\
\plot{pulse00}{width=0.5\textwidth}{Bandpass filter pulse $f$}
\plot{ptpwindl0}{width=\textwidth}{Receiver line  $S(\kappa)$  at $z_r=1$ km for source at $z_s=3$ km, $x_s=3$ km. bulk modulus $\kappa$ with low velocity lens as in Figure \ref{fig:bml0}, $\rho$=1 g/cm$^{3}$. Coarse grid: $dx=dz=20$ m, $dt=$ 8 ms, (2,4) staggered grid scheme. }
% at receiver position $1000 m$ for source at $x=3500$ m, $z=3000$ m}

@@

%\includegraphics[height=1.2in]{Fig/ptpwindl0.pdf}\includegraphics[height=1.2in]{Fig/cgwhestsourceplh0.pdf}\\
\plot{cgwhestsourceplh0}{width=\textwidth}{$\of=\oS(\kappa_0)^{\dagger}d$ for $\kappa_0 \equiv 4.0$ GPa, approx. via CG - $r=2000 m$}

>>>>

A simple example: acoustic transmission inversion - isotropic point radiator (``source'') located at  $\bx=\bx_s$
\begin{equation}
\label{eqn:awept}
\frac{1}{\kappa}\frac{\partial p}{\partial t} = -\nabla \cdot {\bf v} + f(t)\delta(\bx-\bx_s), \,\rho \frac{\partial {\bf v}}{\partial t} = - \nabla p; \,p,{\bf v}=0, t \ll 0
\end{equation}
Bulk modulus is depicted in Figure XXX \ref{fig:bml0}.

%\plot{bml0}{width=\textwidth}{Lens example: target bulk modulus $\kappa$}

@@

%\includegraphics[height=1.5in]{Fig/pulse00.pdf} %\includegraphics[height=1.5in]{Fig/ptpwindl0.pdf}\\
%\plot{pulse00}{width=0.5\textwidth}{Bandpass filter pulse $f$}
%\plot{ptpwindl0}{width=\textwidth}{Receiver line  $S(\kappa)$  at
%$z_r=1$ km for source at $z_s=3$ km, $x_s=3$ km. bulk modulus
%$\kappa$ with low velocity lens as in Figure \ref{fig:bml0}, $\rho$=1 g/cm$^{3}$. Coarse grid: $dx=dz=20$ m, $dt=$ 8 ms, (2,4) staggered grid scheme. }
% at receiver position $1000 m$ for source at $x=3500$ m, $z=3000$ m}

@@

%\includegraphics[height=1.2in]{Fig/ptpwindl0.pdf}\includegraphics[height=1.2in]{Fig/cgwhestsourceplh0.pdf}\\
%%\plot{cgwhestsourceplh0}{width=\textwidth}{$\of=\oS(\kappa_0)^{\dagger}d$ for $\kappa_0 \equiv 4.0$ GPa, approx. via CG - $r=2000 m$}
